### 2021-05-25 Modules/Spatial_IIR-MathDerivations.tex
Final fixes

The gain of the reimpinging signal is denoted as $g$ which encapsulates both propagation related gain and the target's radar cross section (RCS). 
We also place a transmitter at $\vpi{0}$, where the transmitted signal $s$, is reflected back from the target and re-impinges the array with a total delay of $\tau_{\text{pd}}=2R/c$ seconds, denoting $c$ as the propagation velocity of the signal in the medium.

@@

Then, denoting

>>>>

The gain of the reimpinging signal is denoted as $g$ which encapsulates both propagation related attenuation and the target's radar cross section (RCS). 
We also place a transmitter at $\vpi{0}$.
The transmitted signal $s$, is reflected back from the target and re-impinges the array with a total delay of $\tau_{\text{pd}}=2R/c$ seconds, denoting $c$ as the propagation velocity of the signal in the medium.

@@

We also denote

### 2021-05-25 Modules/abstractHebrew.tex
Final fixes

בכך מושגים חסכון באנרגית שידור, מניעת הגעת המידע ליעדים בלתי רצויים, חסינות לרעשים ועוד.

@@

המערך היוניפורמי

@@

בו החיישנים מפוזרים על קו ישר במרחקים קבועים האחד מהשני נחשב למערך הבסיסי בעיבוד המרחבי בשל פשטות העיבוד והיישום שלו.

@@

@@

ידרשו פחות משאבים.

@@

``מהו המקביל המרחבי למסנן בעל התגובה האינסופית?``, שכן בההקשר של מערכי חיישנים, חיסכון במשאבים מתבטא בהוזלה משמעותית ומאפשר את מזעור המערכת.

@@

השיטה השניה שהוצעה היתה הגדרת תתי מערכים (חלקים חופפים מהמערך) כך שאל מוצא כל מערך מתייחסים כאל הסחה זמנית של פלט מערך ייחוס כלשהו.

@@

גישה נוספת, אשר מקורה בעיבוד אותו וידאו 

@@

היות ותגובת המסננים מחזורית בשני התדרים, נוצרים עיוותים בקצוות התגובה התדרית ובנוסף לכך, גם שיטה זו מערבת עיבוד זמני לכן אינה מהווה פתרון מספק לשאלת המחקר.

@@

בנוסף, עולה כי התגובה אינה מושפעת רק מכיוון הגעת גל כמו במסננים המוכרים, אלא גם ממרחק המטרה מהמערך. 

@@

בשלב זה, על מנת לקבוע את משקלות המערך, הוגדרו המרחק וכיוון ההגעה כערכים אותם יש לשערך ובהתאם לכך חושבה מטריצת האינפורמציה 
\textenglish{FIM}.

@@

\textenglish{(ULA)}.

@@

היות ושגיאה זו נובעת מהתדרים הנושאים, הוצע שימוש בלתי תלוי בשני תדרים קרובים תוך נסיון לחלץ את המידע המרחבי מהקשר בין האותות הנקלטים.
הפתרון פשוט וזול יחסית ומגדיל סך הכל את המאמץ החישובי ולא את המערך עצמו.

>>>>

ובכך מושגים חסכון באנרגית שידור, מניעת הגעת המידע ליעדים בלתי רצויים, חסינות לרעשים ועוד.

@@

המערך היוניפורמי הלינארי

@@

בו החיישנים מפוזרים על קו ישר במרחקים קבועים האחד מהשני נחשב למערך הבסיסי בעיבוד המרחבי בשל פשטות העיבוד והניתוח האנליטי שלו.

@@

\textenglish{(IIR)}

@@

ידרשו פחות מקדמים.

@@

``מהו המקביל המרחבי למסנן בעל התגובה האינסופית?``, שכן בהקשר של מערכי חיישנים, חיסכון במשאבים מתבטא בהוזלה משמעותית ומאפשר את מזעור המערכת.

@@

השיטה השניה שהוצעה היתה הגדרת תתי מערכים (חלקים חופפים מהמערך המקורי) כך שאל מוצא כל תת מערך מתייחסים כאל הסחה זמנית של פלט מערך ייחוס כלשהו.

@@

גישה נוספת, אשר מקורה בעיבוד אותות וידאו 

@@

היות ותגובת המסננים מחזורית בשני התדרים, נוצרים עיוותים בקצוות התגובה התדרית ובנוסף לכך, גם שיטה זו מערבת עיבוד זמני ולכן אינה מהווה פתרון מספק לשאלת המחקר.

@@

בנוסף, עולה כי התגובה אינה מושפעת רק מכיוון הגעת הגל כמו במסננים המוכרים, אלא גם ממרחק המטרה מהמערך. 

@@

בשלב זה, על מנת לקבוע את משקלות המערך, הוגדרו המרחק וכיוון ההגעה כערכים אותם יש לשערך ובהתאם לכך חושבה מטריצת אינפורמציית פישר
\textenglish{(FIM)}.

@@

\textenglish{ULA}.

@@

היות ושגיאה זו שקולה לאורך הגל לפיו פועל המערך, הוצע שימוש בלתי תלוי בשני תדרים קרובים תוך נסיון לחלץ את המידע המרחבי מהקשר בין האותות הנקלטים.
הפתרון פשוט וזול יחסית ומגדיל בסך הכל את המאמץ החישובי ולא את המערך עצמו.

### 2021-05-25 Modules/apndx_directivityFit.tex
Final fixes

In the process of simplifying \eqref{eq_D} in order to find the expression for the directivity $\mathcal{D}$, we noticed the results were rational.
Following this observation, we numerically swept various values of $N,r$ pairs, trying find a common expression that fits all results which will enable the formulation of the directivity improvement when using the FB.
In the following, we elaborate on the technicalities of this sweeping process.
\par The first step was to formulate the symbolic expression for $H$.
To this end, we used MATLAB\textsuperscript{\textregistered}'s symbolic toolbox, generating the symbolic response $H$.
Afterwards, the 2D sweep range was set, where as mentioned before, $r$ was set to be of rational values.
In each sweep step, a numerical integration was executed with specific values for $N$ and $r$.
Each result was fitted with it's next closest rational number with the help of MATLAB\textsuperscript{\textregistered}'s \emph{rats} auxiliary command.
After observing the results, we found that all of them obey the same expression as in \eqref{eq_D_result} for any tolerance, which increased the confidence in the suggested expression.
\par The printout of the code is presented as Table.~\ref{table_D} and the text below.
\begin{table}[h!]
    \caption{Performances of Classical ULA and the Proposed Feedback-Beamforming Architecture, with a Gain Mismatch $r$.}
    \centering
    %\resizebox{1\linewidth}{!}
    {
        \begin{tabular}{||c c c c c c c c c c||}
            \hline
            $r \textbackslash N$ & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ [0.5ex] 
            \hline\hline
            1/10     & 19/9  & 29/9  & 13/3  & 49/9  & 59/9  & 23/3  & 79/9  & 89/9  & 11   \\ [1ex] 
            1/5      & 9/4   & 7/2   & 19/4  & 6     & 29/4  & 17/2  & 39/4  & 11    & 49/4 \\ [1ex] 
            1/3      & 5/2   & 4     & 11/2  & 7     & 17/2  & 10    & 23/2  & 13    & 29/2 \\ [1ex] 
            1/2      & 3     & 5     & 7     & 9     & 11    & 13    & 15    & 17    & 19   \\ [1ex] 
            5/8      & 11/3  & 19/3  & 9     & 35/3  & 43/3  & 17    & 59/3  & 67/3  & 25   \\ [1ex] 
            3/4      & 5     & 9     & 13    & 17    & 21    & 25    & 29    & 33    & 37   \\ [1ex] 
            4/5      & 6     & 11    & 16    & 21    & 26    & 31    & 36    & 41    & 46   \\ [1ex] 
            \hline
         \end{tabular}
     }
    \label{table_D}
\end{table}
\section*{MATLAB\textsuperscript{\textregistered} Code}
\lstinputlisting[style=mcode]{Modules/directivityAnalysis.m}

>>>>

In the process of simplifying \eqref{eq_D} in order to find the expression for the directivity $\mathcal{D}$, we noticed the results were a rational expression.
Following this observation, we numerically swept various values of $N,r$ pairs, trying find a common expression that fits all results which will enable the formulation of the directivity improvement when using the FB.
In the following, we elaborate on the technicalities of this sweeping process.
\par The first step was to formulate the symbolic expression for $H$.
To this end, we used MATLAB\textsuperscript{\textregistered}'s symbolic toolbox, generating the symbolic response $H$.
Afterwards, the 2D sweep range was set, where as mentioned before, $r$ was set to be of rational values.
In each sweep step, a numerical integration was executed with specific values for $N$ and $r$.
Each result was fitted with it's next closest rational number with the help of MATLAB\textsuperscript{\textregistered}'s \emph{rats} auxiliary command.
After observing the results, we found that all of them obey the same expression as in \eqref{eq_D_result} for any tolerance, which increased the confidence in the suggested expression.
\par The printout of the code is presented as Table.~\ref{table_D} and the text below.
\begin{table}[h!]
    \caption{Performances of Classical ULA and the Proposed Feedback-Beamforming Architecture, with a Gain Mismatch $r$.}
    \centering
    %\resizebox{1\linewidth}{!}
    {
        \begin{tabular}{||c c c c c c c c c c||}
            \hline
            $r \textbackslash N$ & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ [0.5ex] 
            \hline\hline
            1/10     & 19/9  & 29/9  & 13/3  & 49/9  & 59/9  & 23/3  & 79/9  & 89/9  & 11   \\ [1ex] 
            1/5      & 9/4   & 7/2   & 19/4  & 6     & 29/4  & 17/2  & 39/4  & 11    & 49/4 \\ [1ex] 
            1/3      & 5/2   & 4     & 11/2  & 7     & 17/2  & 10    & 23/2  & 13    & 29/2 \\ [1ex] 
            1/2      & 3     & 5     & 7     & 9     & 11    & 13    & 15    & 17    & 19   \\ [1ex] 
            5/8      & 11/3  & 19/3  & 9     & 35/3  & 43/3  & 17    & 59/3  & 67/3  & 25   \\ [1ex] 
            3/4      & 5     & 9     & 13    & 17    & 21    & 25    & 29    & 33    & 37   \\ [1ex] 
            4/5      & 6     & 11    & 16    & 21    & 26    & 31    & 36    & 41    & 46   \\ [1ex] 
            \hline
         \end{tabular}
     }
    \label{table_D}
\end{table}
\section*{MATLAB\textsuperscript{\textregistered} Code}
\lstinputlisting[style=mcode]{Modules/directivityAnalysis.m}

### 2021-05-25 Modules/paper_sec_prlms.tex
Final fixes

Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to the convectional beamformer (CB) beamformer.

@@

            \put (24.25, 50){\footnotesize{$x_{0}$}}
            \put (35, 50){\footnotesize{$x_{1}$}}
            \put (55, 50){\footnotesize{$x_{N-1}$}}

@@

            \put (58, 58){\footnotesize{$\vpi{N-1}$}}
            \put (37, 58){\footnotesize{$\vpi{1}$}}
            \put (26.5, 58){\footnotesize{$\vpi{0}$}}

@@

Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see App.~\ref{apndx_directivityFit} and the complementary Fig.~\ref{fig_directivity}) we suggest to approximate the directivity with 

@@

    \caption{Performances of Classical ULA and the Proposed Feedback-Beamforming Architecture, with a Gain Mismatch $r$.}

@@

            & ULA & \thead{FEEDBACK\\BEAMFORMING} & IMPROVEMENT \\ [0.5ex] 

@@

In Table.~\ref{table_arrayPerfEmp} we show the coherency between the results and the performance related expressions of Table.~\ref{table_arrayPerformance}.

>>>>

Note that setting $\vAlpha=\vecnot{0}$ (i.e., cancelling the feedback) degenerates the system to the conventional beamformer (CB).

@@

            \put (27, 53){\footnotesize{$x_{N-1}$}}
            \put (37.5, 53){\footnotesize{$x_{N-2}$}}
            \put (58, 53){\footnotesize{$x_{0}$}}

@@

            \put (60, 60.5){\footnotesize{$\vpi{0}$}}
            \put (39, 60.5){\footnotesize{$\vpi{N-2}$}}
            \put (28, 60.5){\footnotesize{$\vpi{N-1}$}}

@@

Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see App.~\ref{apndx_directivityFit} and the complementary Fig.~\ref{fig_directivity} and Fig.~\ref{fig_directivityErr}) we suggest to approximate the directivity with 

@@

    \caption{Performances of CB and the Proposed Feedback-Beamforming Architecture, with a Gain Mismatch $r$.}

@@

            & CB & \thead{FEEDBACK\\BEAMFORMING} & IMPROVEMENT \\ [0.5ex] 

@@

In Table.~\ref{table_arrayPerfEmp} we show the consistency between the results and the performance related expressions of Table.~\ref{table_arrayPerformance}.

### 2021-05-25 Modules/sec_FIM_and_CRLB.tex
Final fixes

This choice of weights may be interpreted as a generalized version of the conventional beamformer (CB) \cite{van2004optimum}. 

>>>>

Considering narrowband signals, this choice of weights may be interpreted as a generalized version of the CB \cite{van2004optimum} which is a mere coherent summation of the feedback signal.
% \begin{figure}[t!]
%     \begin{center}
%         \begin{overpic}[width=0.55\linewidth, 
%         % grid, 
%         tics=10,trim=0 0 0 0]{./Media/fig_CB_vanTrees.PNG}
%             % \put (20, 23){\rotatebox{0}{\footnotesize{Angular response}}}
%         \end{overpic}
%     \end{center}
%     \caption{
%     % A visualization of the spatial area selectivity concept.
%     The CB - time shifting the input signals as if the impinging wave from a certain DOA arrives from the array's boresight.
%     \label{fig_CB_vanTrees}
% \end{figure}

### 2021-05-25 Modules/sec_conclusions_LOCAL.tex
Final fixes

In this work we have suggested a novel approach to beamforming and localization, which is based on a generating a continuous feedback between the array and the target of interest.
Integrating feedback into standard beamformers proved to achieve the spatial domain equivalent of the temporal IIR filtering.
It seems that a simple generalization of the conventional-beamformer maximizes (locally) the system's spatial information, thus enabling high localization accuracy.
The feedback-based architecture performance evaluation predicts an unlimited improvement in all criteria, when considering perfect knowledge of the target's range and the channel attenuation.
It turns out that a single frequency waveform based feedback-beamformer is impractical, being too sensitive to even mild target range estimation errors.
Fortunately, using a DF waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
Also, the DF scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.
\par In the following, we overview some interesting leads for future study of the FB concept.

>>>>

In this work we have suggested a novel approach to beamforming and localization, which is based on generating a continuous feedback between the array and the target of interest.
Integrating feedback into standard beamformers proved to achieve the spatial domain equivalent of the temporal IIR filtering.
It seems that a simple generalization of the conventional-beamformer maximizes (locally) the system's spatial information, thus enabling high localization accuracy.
The feedback-based architecture performance evaluation predicts an unlimited improvement in all criteria, when considering perfect knowledge of the target's range and channel attenuation.
It turns out that a single frequency waveform based feedback-beamformer is impractical, being too sensitive to even mild target range estimation errors.
Fortunately, using a DF waveform and applying simple frequency domain manipulations to the output and feedback signals, was found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
Also, the DF scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.
\par In the following, we overview some interesting leads for future study of the FB concept.

### 2021-05-25 Modules/sec_future_dynamic.tex
Final fixes

Revisiting \eqref{eqn:SingleSensorTemporalEquality}, a natural initial generalization would be to allow the target of interest to be dynamic, i.e. introducing a general 3D arbitrary target location $\vecnot{p}_{t}\rBrace{t}$.
The location dynamics may be represented in terms of dynamic propagation delay, $\tau_{pd}\rBrace{t}$ and Doppler.
% It follows that an auxiliary temporal quantity should be defined, which for a given impinging signal, expresses it's transmission time.
\par
Following the basic steps of temporal analysis, as in Chapter.~\ref{chap:firstchap}, starts with expressing the impinging signal of a single sensor.
As in the analysis of static target scenario, the signal consists of two contributions, i.e. the reflected emitted signal and the reflected feedback signal.
Therefore, for each moment $t$, we should resolve the corresponding moment in which the current impinging signals were emitted by the array.
\par
To this end, we first denote $t_{\text{ref}}\rBrace{t}$ the moment in which the currently impinging signal was reflected by the target of interest.
Another auxiliary quantity is reflection moment's corresponding target range $\tau_{\text{ref}}$ where the following relation holds
\begin{equation}
\label{eq_tRef_relation}
    t-\frac{R\rBrace{t_{\text{ref}}\rBrace{t}}}{c} = t_{\text{ref}}\rBrace{t}.
\end{equation}
Assuming $t_{\text{ref}}\rBrace{t}$ is resolved, we denote the propagation delay at the reflection moment $\tau_{\text{ref}}\rBrace{t} = R\rBrace{t_{\text{ref}}\rBrace{t}}/c$ and express the emission moment as
\begin{equation}
\label{eq_tTX}
    t_{\text{\tiny{TX}}}\rBrace{t} 
    = 
    t_{\text{ref}}\rBrace{t} - \tau_{\text{ref}}\rBrace{t} 
    =
    t - 2\tau_{\text{ref}}\rBrace{t}.
\end{equation}
With $t_{\text{\tiny{TX}}}$, we rewrite \eqref{eqn:SingleSensorTemporalEquality} as
\begin{equation}
    \label{eq_fut_dyn_temp}
    x_{n}(t) = g\rBrace{s\rBrace{t_{\text{\tiny{TX}}}\rBrace{t}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t_{\text{\tiny{TX}}}\rBrace{t}}}}.
\end{equation}
\par
Obviously, to have a closed form expression for $x_{n}(t)$, there should be a model for the target's dynamics (i.e. $\vpt{}$).
Such an example, is a target with constant radial (constant DOA) velocity $v$ with respect to the array which is initially positioned with distance of $R_{0}$ from the array.
It follows that
\begin{equation}
    \label{eq_fut_constV_Rt}
    R\rBrace{t} = R_{0} + vt
\end{equation}
which when plugged into \eqref{eq_tRef_relation} gives rise to
\begin{equation}
    \label{eq_fut_constV_ti}
    t_{\text{\tiny{TX}}}\rBrace{t}=\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}
\end{equation}
and it follows that
\begin{equation}
    \label{eq_fut_constV_xn}
    x_{n}(t) = g\vBrace{s\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}}}.
\end{equation}
Then, similar steps as in Sec.~\ref{sec_introduceFeedback} are to be made to get an expression for the system's response $H$.
It is expected that as in RADAR systems, the tracking of the object should now also take Doppler shifts into account.
% One may consider the following research approaches for further investigation
% \begin{itemize}
%     \item \textbf{Modeling of target's location}
%     \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{\text{\tiny{TX}}}$, $$t_{\text{\tiny{TX}}}=\frac{R\rBrace{t=0}+\rBrace{c+v_{\theta}}t}{c},$$ where $R\rBrace{t=0}$ is the initial distance to the target of interest and further development may lead to a closed form response like in the stationary case.
%     In this manner, other components may be added to the positional equation.
%     \item \textbf{Frame based processing}
%     \\Considering low velocity of the target with respect to the wave's propagation's speed, one may consider treating the processor as pseudo-stationary and explore its implications for increasing velocities/processing duration. 
% \end{itemize}

>>>>

Revisiting \eqref{eqn:SingleSensorTemporalEquality}, a natural initial generalization would be to allow the target of interest to be dynamic, i.e. introducing a general 3D arbitrary target location $\vecnot{p}_{t}\rBrace{t}$.
The location dynamics may be represented in terms of dynamic propagation delay, $\tau_{pd}\rBrace{t}$ and Doppler.
% It follows that an auxiliary temporal quantity should be defined, which for a given impinging signal, expresses it's transmission time.
\par
Following the basic steps of temporal analysis, as in Chapter.~\ref{chap:firstchap}, we start with expressing the impinging signal of a single sensor.
As in the analysis of static target scenario, the signal consists of two contributions, i.e. the reflected emitted signal and the reflected feedback signal.
Therefore, for each moment $t$, we should resolve the corresponding moment in which the current impinging signals were emitted by the array.
\par
To this end, we first denote $t_{\text{ref}}\rBrace{t}$ as the moment in which the currently impinging signal was reflected by the target of interest.
Another auxiliary quantity is the reflection moment's corresponding target range $\tau_{\text{ref}}$ where the following relation holds
\begin{equation}
\label{eq_tRef_relation}
    t-\frac{R\rBrace{t_{\text{ref}}\rBrace{t}}}{c} = t_{\text{ref}}\rBrace{t}.
\end{equation}
Assuming $t_{\text{ref}}\rBrace{t}$ is resolved, we denote the propagation delay at the reflection moment $\tau_{\text{ref}}\rBrace{t} = R\rBrace{t_{\text{ref}}\rBrace{t}}/c$ and express the emission moment as
\begin{equation}
\label{eq_tTX}
    t_{\text{\tiny{TX}}}\rBrace{t} 
    = 
    t_{\text{ref}}\rBrace{t} - \tau_{\text{ref}}\rBrace{t} 
    =
    t - 2\tau_{\text{ref}}\rBrace{t}.
\end{equation}
With $t_{\text{\tiny{TX}}}$, we rewrite \eqref{eqn:SingleSensorTemporalEquality} as
\begin{equation}
    \label{eq_fut_dyn_temp}
    x_{n}(t) = g\rBrace{s\rBrace{t_{\text{\tiny{TX}}}\rBrace{t}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t_{\text{\tiny{TX}}}\rBrace{t}}}}.
\end{equation}
\par
Obviously, to have a closed form expression for $x_{n}(t)$, there should be a model for the target's dynamics (i.e. $\vpt{}$).
Such an example, is a target with constant radial (constant DOA) velocity $v$ with respect to the array which is initially positioned with distance of $R_{0}$ from the array.
It follows that
\begin{equation}
    \label{eq_fut_constV_Rt}
    R\rBrace{t} = R_{0} + vt
\end{equation}
which when plugged into \eqref{eq_tRef_relation} gives rise to

\begin{equation}
    \label{eq_fut_constV_ti}
    %\resizebox{.89\linewidth}{!}{
    \begin{split}
        t_{\text{ref}}\rBrace{t} &= \frac{c}{c+v}t-\frac{R_{0}}{c+v} \\
        \tau_{\text{ref}}\rBrace{t} &= \frac{R_{0}+vt}{c+v} \\
        t_{\text{\tiny{TX}}}\rBrace{t} &= t-2\tau_{\text{ref}}\rBrace{t} \\ 
        &= \frac{c-v}{c+v}t-\frac{2R_{0}}{c+v} \\
    \end{split}
\end{equation}

and it follows that
\begin{equation}
    \label{eq_fut_constV_xn}
    x_{n}(t) = g\vBrace{s\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{\frac{c-v}{c+v}t-\frac{2R_{0}}{c+v}}}}.
\end{equation}
Then, similar steps as in Sec.~\ref{sec_introduceFeedback} are to be made to get an expression for the system's response $H$.
It is expected that as in RADAR systems, the tracking of the object should now also take Doppler shifts into account.
% One may consider the following research approaches for further investigation
% \begin{itemize}
%     \item \textbf{Modeling of target's location}
%     \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{\text{\tiny{TX}}}$, $$t_{\text{\tiny{TX}}}=\frac{R\rBrace{t=0}+\rBrace{c+v_{\theta}}t}{c},$$ where $R\rBrace{t=0}$ is the initial distance to the target of interest and further development may lead to a closed form response like in the stationary case.
%     In this manner, other components may be added to the positional equation.
%     \item \textbf{Frame based processing}
%     \\Considering low velocity of the target with respect to the wave's propagation's speed, one may consider treating the processor as pseudo-stationary and explore its implications for increasing velocities/processing duration. 
% \end{itemize}

### 2021-05-25 Modules/sec_future_multiTarget.tex
Final fixes

Considering practical scenarios of multiple ($P$) targets, positioned in $p_{t_,i}\ \forall i\in0\dots{}P-1$, the obvious generalization of \eqref{eqn:SingleSensorTemporalEquality} is 
\begin{equation}
    \label{eqn:ftr_dyn_temp}
    x_{n}(t) = \sum_{i=0}^{i=P-1}{\vBrace{g\rBrace{s\rBrace{t-\tau_{pd,i}-\tau_{n,i}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd,i}-\tau_{n,i}}}}}},
\end{equation}
where $\tau_{pd,i}$ is the delay of the signal which reflected from $p_{t,i}$.
Interesting directions of research may include
\begin{itemize}
    \item The effects of closely positioned targets
    \item Localization resolution
    \item Maximal number of simultaneously detected targets with respect to N
    \item Independent beamforming per target with multiple transmitters steering the feedback signal. 
\end{itemize}

>>>>

Considering practical scenarios of multiple ($P$) targets, positioned in $p_{t_,i}\ \forall i\in0\dots{}P-1$, the obvious generalization of \eqref{eqn:SingleSensorTemporalEquality} is 
\begin{equation}
    \label{eqn:ftr_dyn_temp}
    x_{n}(t) = \sum_{i=0}^{P-1}{\vBrace{g\rBrace{s\rBrace{t-\tau_{pd,i}-\tau_{n,i}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd,i}-\tau_{n,i}}}}}},
\end{equation}
where $\tau_{pd,i}$ is the delay of the signal which reflected from $p_{t,i}$.
Interesting directions of research may include
\begin{itemize}
    \item The effects of closely positioned targets
    \item Localization resolution
    \item Maximal number of simultaneously detected targets with respect to N
    \item Independent beamforming per target with multiple transmitters steering the feedback signal. 
\end{itemize}
